The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-04 src/ms.tex
Add Leo to LIGO et al
Co-authored-by: Leo Singer <leo.p.singer@nasa.gov>
add CRT at the end of the document
Update ms.tex
remove example
latex en dash

JWST
\secunfilled

@@

\section{Future Plans for the Astropy Project} \label{sec:future}

@@

The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.  We would like acknowledge the support of the
Space Telescope Science Institute, Harvard–Smithsonian Center for Astrophysics,
and the South African Astronomical Observatory.

>>>>

JWST
\secauthor{Larry Bradley}

@@

LIGO/Virgo/KAGRA
\secauthor{Leo Singer}
\section{Future Plans for the Astropy Project} \label{sec:future}

@@

The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.  We would like acknowledge the support of the
Space Telescope Science Institute, Harvard--Smithsonian Center for Astrophysics,
and the South African Astronomical Observatory.
